Variants on the Flight and Maintenance Planning problem

### 2019-04-12 latex/notes/model/model.tex
reformulation of flight hours in latex.

    The following decision variables control the used and remaining flight time in aircraft.

    \begin{tabular}{p{8mm}p{117mm}}
        $u_{it}$    &  flown time (continuous) by aircraft $i \in I$ during period $t \in \mathcal{T}$. \\        
        $rft_{it}$  &  remaining flight time (continuous) for aircraft $i \in I$ at the end of period $t \in \mathcal{T}$. \\  
    \end{tabular}

@@

    \begin{align}
        & \text{Min}\; \sum_{i \in \mathcal{I}, t_1 \in \mathcal{T}^{M_{Init}}_i, t_2 \in \mathcal{T}^M_{t_1} - |\mathcal{T}|} m_{it_1t_2}  \label{eq:objective1}\\
        & \text{Min}\; \sum_{i \in \mathcal{I}, t_1 \in \mathcal{T}^{M_{Init}}_i, t_2 \in \mathcal{T}^M_{t_1}} m_{it_1t_2} \times H^{max} - \sum_{i \in \mathcal{I}} rft_{i|\mathcal{T}|} \label{eq:objective2}
    \end{align}

@@

    \begin{align}
       & \sum_{i \in \mathcal{IK}_k, (t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{T}_{t}} m_{it_1t_2} + N^{Clust}_{kt} \leq A^{Clust}_{kt}
        &k \in \mathcal{K}, t \in \mathcal{T} \label{eq:serviceability-cluster} \\
       & \sum_{i \in \mathcal{IK}_k} rft_{it} \geq H^{Clust}_{kt}
        &k \in \mathcal{K}, t \in \mathcal{T} \label{eq:sustainability-cluster}
    \end{align}

@@

    \begin{align}
        % remaining used time
         & u_{it} \geq \sum_{j \in \mathcal{JT}_t \cap \mathcal{JI}_i} \sum_{(t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{J}_{jt}} a_{ijt_1t_2} H_j 
            & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:flight1}\\
         & u_{it} \in [U^{min}, \max_j{\{H_j\}}]
            & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:flight_lower}\\
         & rft_{it} \leq rft_{i(t-1)} + H^{max} \sum_{(t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{T}_{t}} m_{it_1t_2} - u_{it}
            & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:rft_upper}\\
        & rft_{i0} = Rft^{Init}_i
               & i \in \mathcal{I} \label{eq:rft_initial}\\
        & rft_{it} \geq H^{max} \sum_{(t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{T}_{t}} m_{it_1t_2}
                &t \in \mathcal{T}, i \in \mathcal{I}\label{eq:rft_lower}\\
        & rft_{it} \in [0,H^{max}]
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:mu}
    \end{align}

        % These constraints calculate the balances of hours for each aircraft.
    The flight time per aircraft and period is calculated in (\ref{eq:flight1})-(\ref{eq:flight_lower}). The remaining flight time is defined by (\ref{eq:rft_upper})-(\ref{eq:rft_initial}) and its limits by (\ref{eq:rft_lower})-(\ref{eq:mu}).

>>>>

    % The following decision variables control the used and remaining flight time in aircraft.

    % \begin{tabular}{p{8mm}p{117mm}}
    %     $u_{it}$    &  flown time (continuous) by aircraft $i \in I$ during period $t \in \mathcal{T}$. \\        
    %     $rft_{it}$  &  remaining flight time (continuous) for aircraft $i \in I$ at the end of period $t \in \mathcal{T}$. \\  
    % \end{tabular}

@@

    \begin{align}
        & \text{Min}\; \sum_{i \in \mathcal{I}, t_1 \in \mathcal{T}^{M_{Init}}_i, t_2 \in \mathcal{T}^M_{t_1} - |\mathcal{T}|} m_{it_1t_2}  \label{eq:objective1}\\
        % & \text{Min}\; \sum_{i \in \mathcal{I}, t_1 \in \mathcal{T}^{M_{Init}}_i, t_2 \in \mathcal{T}^M_{t_1}} m_{it_1t_2} \times H^{max} - \sum_{i \in \mathcal{I}} rft_{i|\mathcal{T}|} \label{eq:objective2}
    \end{align}

@@

    \begin{align}
       & \sum_{i \in \mathcal{IK}_k, (t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{T}_{t}} m_{it_1t_2} + N^{Clust}_{kt} \leq A^{Clust}_{kt}
        &k \in \mathcal{K}, t \in \mathcal{T} \label{eq:serviceability-cluster} \\
       % & \sum_{i \in \mathcal{IK}_k} rft_{it} \geq H^{Clust}_{kt}
       %  &k \in \mathcal{K}, t \in \mathcal{T} \label{eq:sustainability-cluster}
    \end{align}

@@

    \begin{align}
        % remaining used time
        %  & u_{it} \geq \sum_{j \in \mathcal{JT}_t \cap \mathcal{JI}_i} \sum_{(t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{J}_{jt}} a_{ijt_1t_2} H_j 
        %     & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:flight1}\\
        %  & u_{it} \in [U^{min}, \max_j{\{H_j\}}]
        %     & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:flight_lower}\\
        %  & rft_{it} \leq rft_{i(t-1)} + H^{max} \sum_{(t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{T}_{t}} m_{it_1t_2} - u_{it}
        %     & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:rft_upper}\\
        % & rft_{i0} = Rft^{Init}_i
        %        & i \in \mathcal{I} \label{eq:rft_initial}\\
        % & rft_{it} \geq H^{max} \sum_{(t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{T}_{t}} m_{it_1t_2}
        %         &t \in \mathcal{T}, i \in \mathcal{I}\label{eq:rft_lower}\\
        % & rft_{it} \in [0,H^{max}]
        %         & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:mu}
        & \sum_{(j, t, t') \in \mathcal{J}\mathcal{T}\mathcal{T}_{a1t_1}} a_{ijtt'} H'_{jtt'} + U^{min}_{1t_1} \leq Rft^{Init}_i + H^{max} (1 - m_{it_1t_2}) 
                & t_1 \in \mathcal{T}, t_2 \in \mathcal{T}^M_{t_1}, i \in \mathcal{I}\label{eq:cycle_hours1}\\
        & \sum_{(j, t, t') \in \mathcal{J}\mathcal{T}\mathcal{T}_{at_1t_2}} a_{ijtt'} H'_{jtt'} + U^{min}_{t_1t_2} \leq H^{max} + H^{max} (1 - m_{it_1t_2}) 
                & t_1 \in \mathcal{T}, t_2 \in \mathcal{T}^M_{t_1}, i \in \mathcal{I}\label{eq:cycle_hours2}\\
        & \sum_{(j, t, t') \in \mathcal{J}\mathcal{T}\mathcal{T}_{at_2|\mathcal{T}|}} a_{ijtt'} H'_{jtt'} + U^{min}_{t_2|\mathcal{T}|} \leq H^{max} + H^{max} (1 - m_{it_1t_2}) 
                & t_1 \in \mathcal{T}, t_2 \in \mathcal{T}^M_{t_1}, i \in \mathcal{I}\label{eq:cycle_hours3}
    \end{align}

        % These constraints calculate the balances of hours for each aircraft.
    % The flight time per aircraft and period is calculated in (\ref{eq:flight1})-(\ref{eq:flight_lower}). The remaining flight time is defined by (\ref{eq:rft_upper})-(\ref{eq:rft_initial}) and its limits by (\ref{eq:rft_lower})-(\ref{eq:mu}).
